\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\usepackage{amsfonts} 
\usepackage{amssymb}

\begin{document}

\title{Gödelfish}
\author{https://esolangs.org/wiki/User:Salpynx}

\maketitle

\begin{abstract}
The abstract text goes here.
\end{abstract}

\section{Introduction}
Gödelfish is a Gödel numbering for the esoteric programming language Deadfish. It also provides a range of output encodings for the results of executing the code.

A Gödelfish program, $\ddot{\varphi}$, can be formed from a Deadfish program by making the following subtitutions and interpreting the result as a base4 numeral.

\begin{table}[h!]
  \begin{center}
    \caption{Gödel numbering.}
    \label{tab:table1}
    \begin{tabular}{c|c} % <-- Changed to S here.
      \textbf{Deadfish} & \textbf{Gödelfish (base4)} \\
      \hline
      d & 0\\
      i & 1\\
      s & 2\\
      o & 3\\
    \end{tabular}
  \end{center}
\end{table}

\section{Conversion to Brainfoctal}

A Gödelfish program, $\ddot{\varphi}$, can be converted to a corresponding Brainfoctal (a Turing complete Gödel numbering language) value, $\beta$, using the following bijective continuous piecewise linear function:

\[
b:\mathbb{R} \to \mathbb{N} \text{ given by }
b(\ddot{\varphi}) = \beta
\]

\[
b^{-1}:\mathbb{N} \to \mathbb{R} \text{ given by }
b^{-1}(\beta) = \ddot{\varphi}
\]

\begin{equation}
	b(\ddot{\varphi}) = \sum_{i=0}^{\lfloor \log_4 \ddot{\varphi} \rfloor + 1} 8^{\sum_{j=0}^{i} \lfloor \log_8(8^{136}c(\lfloor{\frac{\ddot{\varphi}}{4^j}}\rfloor \bmod 4) + q) \rfloor + 1} 8^{136}c(\lfloor{\frac{\ddot{\varphi}}{4^i}}\rfloor \bmod 4) + q
\end{equation}

\begin{equation}
	c(x) = 8^{136} ( 4 + 216x + \lfloor {\frac{x}{2}} (p - 2 \cdot 216) \rfloor + \lfloor {\frac{x}{3}} r .... \rfloor ) + q
\end{equation}

\[
	p = 311138260380880706729590840158768308142226
\]
\[
	q = 592854091379476160373099716865089354963626327670769972503843485670491819724574514810292068238714291637482209552473531334722
\]
\[
	r = {\frac{23955826966570484256306562472764680810624019453460258257506148662886330202100027735819081798905623824670875086665797446363726141753333684743611573092884160}{8^{136}}}-q
\]
\[
	c(d) =
		\begin{cases}
			4,& \text{if } d \lessapprox 1.9 \\
			216,& \text{if } d \gtrapprox 1.9 \\
		\end{cases}
\]





This converted number can then be executed as Brainfoctal, and will produce the expected Deadfish output.

\subsection{Variants}
There are two variants of Gödelfish.

$\ddot{\varphi} \in \mathbb{N}$: \textit{Natural} Gödelfish.

$\ddot{\varphi} \in \mathbb{R}$: \textit{Real} Gödelfish.

Where
$\ddot{\varphi} \in (\mathbb{R} - \mathbb{N})$ can be termed \textit{Unatural} Gödelfish.


\section{Gödelfish Code Generation}
The following function generates a Gödelfish program that sets the accumulator to $i, \text{where } i \in \mathbb{N}_{i\ne256}$:

\[
\phi(i) = \frac{4^{\frac{\lvert\alpha(i)\rvert + \alpha(i)}{2}} - 1}{3} 
+ \gamma(i)(38^2 + 2)4^{\lvert i-17^2\rvert}
+ \frac{0}{(4^4 - i)(\lvert i \rvert + i)}
\]
where
\[
\alpha(i) = i \big\lvert 1-\gamma(i) \big\rvert
+ \gamma(i)(i - 17^{2})
\]
and
\[
\gamma: \mathbb{N} \to \{0, 1\} \text{ given by } \gamma(i) = \left\lceil\frac{i - 4^{4}}{1 + (i - 4^{4})^{2}}\right\rceil
\]


This is by no means an optimised conversion, but it does produce accurate output for all valid inputs.
There are other possible code generation functions.


To modify a program to output the accumulator value, simply multiply by 4, and add 3:

\[
	\ddot{\varphi}_{\textsc{output}} = 4\phi(i) + 3
\]

\section{Evaluation and output encoding}


\begin{equation}
    \label{simple_equation}
    \alpha = \sqrt{ \beta }
\end{equation}


\section{Conclusion}
Gödelfish is TG.

\end{document}
